---
name: Dr. Micheline Campbell
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons), PhD
position: Research Associate, UNSW Sydney
address: Sydney, Australia
phone: +61 411 282 657
email: michelineleecampbell@gmail.com
# website: michelinecampbell.netlify.app
github: MichelineCampbell
# twitter: michcampbell
# pronouns: she

# mastodon: michcampbell
# headcolor: 990000
headcolor: 125656
# headcolor: 000000
# date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::moderncv:
    theme: classic
    keep_tex: true
  # vitae::awesomecv
    # latexengine: pdflatex

    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(readr)
library(tidyverse)
library(glue)
library(lubridate)
```

# Professional summary

I have a PhD in Geography, and my thesis focused on speleothem palaeoclimatology using samples from the Snowy Mountains, Australia. My research interests have continued to be based in Quaternary science, but while I have maintained my interest in stalagmite-derived climate proxy data, I have also worked in surface hydrology and the palaeoclimate-water security nexus. I am currently employed as a research associate at the University of New South Wales, contributing to the Australian Research Council Discovery Project "Reconstructing Australia’s fire history from cave stalagmites". I am hoping to secure a position which will allow me to continue to develop my analytical skillset, in both the laboratory and in data science, as well as continue to support the next generation of earth and environmental scientists. 

<!-- I am hoping to continue my career in physical geography by securing a position where I can apply skills I have developed in a meaningful way and contribute to the development of the next generation of geographers. -->

# Education
```{r edu1, include = FALSE}

edu.raw <- read_csv("data/education.csv")

edu.raw <- edu.raw %>%
  mutate(start_date=as.Date(start_date, format = "%d/%m/%Y")) %>%
  mutate(end_date=as.Date(end_date, format = "%d/%m/%Y")) %>%
  arrange(desc(end_date))


edu1 <- which(is.na(edu.raw$thesis))
edu2 <- edu.raw[-edu1,]

edu3 <- edu2 %>%
  mutate(pi = dplyr::if_else(!is.na(pi), glue("Supervisors: {pi}"), "Supervisor: NA"),
         thesis = dplyr::if_else(!is.na(thesis), glue(" \\textbf{Thesis: [thesis]}", .open = "[", .close = "]"),glue(NA))) %>%
  gather(thesis, pi, key = "whytype", value = "why") %>%
    arrange(desc(end_date))
edu3["why"]

edu4 <- edu.raw[edu1,]
```

```{r edu2}

detailed_entries(edu3,
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} -
           {if_else(!is.na(end_date),
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = paste(department, university, sep = ", "),
                 #why = why,
                 .protect = FALSE)
detailed_entries(edu4,
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} -
           {if_else(!is.na(end_date),
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 .protect = FALSE)
```

# Experience

## Research

```{r experience}
job.titles <- read_csv("data/experience.csv")
job.descriptions <- read_csv("data/jobdesc.csv")

job.titles <- job.titles %>%
  mutate(begin=as.Date(begin, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))


job.titles %>%
  # Only 5 most recent jobs
  arrange(desc(begin)) %>%
  filter(row_number() <= 5) %>%
  # Join job descriptions
  left_join(job.descriptions) %>%
  # Arrange by descending begin date
  arrange(desc(begin)) %>%
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = glue("{dept}, {where}"),
    where = glue("{city}, {state}, {country}"),
    why = accomplishments)


```

## Teaching
```{r teaching}
fund <- read_csv("data/teaching.csv")

detailed_entries(fund,
                 when = years,
                 what = paste(role, course, sep = ": "),
                 where = location,
                 with = paste(department, university, sep = ", "),
                 .protect = FALSE) %>%
  arrange(desc(when))
```
Teaching contributions include the delivery and creation of content for undergraduate and masters level units, both in the classroom/laboratory and in the field. Catchment and River Processes is a field-based course which I taught into for my entire time at UWA, and which I co-coordinated in 2018. 


<!-- \newpage -->
# Grants and Awards
```{r funding}
fund <- read_csv("data/funding.csv")

detailed_entries(fund,
                 when = years,
                 what = paste(funder, grant),
                 why = amount,
                 where = leader,
                 .protect = FALSE) %>%
  arrange(desc(when))

```

<!-- \newpage -->
# Publications

```{r publications}
# add in review
bibliography_entries("data/my_pubs.bib") %>%
 dplyr::arrange(desc(issued)) # bib from 'my_pubs' folder in Mendeley
```

## Publications in review

```{r inreview}
bibliography_entries("data/pubs_in_review.bib") %>%
 dplyr::arrange(desc(issued)) # bib from 'my_pubs' folder in Mendeley

```

<!-- \newpage -->

# Media and reports

```{r media}

bibliography_entries("data/media.bib") %>%
 dplyr::arrange(desc(issued))

```


<!-- \newpage -->
# Presentations (presenting only)
```{r presentations, include =FALSE}
presentations.raw <- read_csv("data/presentations.csv")
presentations <-
  presentations.raw %>%
  mutate(when=as.Date(when, format = "%d/%m/%Y")) %>%
  arrange(desc(when))

```

## Talks
```{r talks}
presentations %>%
  filter(tag %in% c("talk")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)

```

\newpage

## Posters
```{r posters}
presentations %>%
  filter(tag %in% c("poster")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)
```

## Seminars

```{r seminars}
presentations %>%
  filter(tag %in% c("seminar")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)
```


<!-- \newpage -->
# Skills

## Statistical

```{r softsskills}
skills.titles <- read.csv("data/skills.csv")
skills.descriptions <- read.csv("data/skillsdesc.csv")

skills.titles %>%
  dplyr::filter(., include == "Y") %>%
  dplyr::filter(tag %in% c("stats1")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

```{r methodskills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("stats2")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

## Field
```{r fieldskills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("field")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

## Laboratory
```{r labskills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("lab")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

<!-- \newpage -->
## Other
```{r otherkills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("other")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```
<!-- \newpage -->
# Service 

```{r servics} 
service.titles <- read_csv("data/service.csv")
service.descriptions <- read_csv("data/servicedesc.csv")

service.titles <- service.titles %>%
  mutate(start = as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end = as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end)) 



service.descriptions <- service.descriptions %>%
  mutate(start=as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))

service.titles %>%
  arrange(desc(start)) %>%
  # Join job descriptions
  left_join(service.descriptions) %>%
  # Arrange by descending begin date
  arrange(desc(start)) %>%
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(start, label = TRUE, abbr = TRUE)} {year(start)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'Present')}")),
    
    
    
    # when = as.character(
#       glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} -
#            {if_else(!is.na(end),
#            paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    why = accomplishment)


```

# Completed peer reviews

```{r reviews}
revs <- read_csv("data/reviews.csv")

revs <- revs %>%
  filter(., include == "Y") %>%
  arrange(desc(year)) 
         # end = as.character(end))



brief_entries(revs,
  what = group,
  when = year)

```


# Professional development
```{r pd}
pd <- read_csv("data/pd.csv")

pd <- pd %>%
  filter(., include == "Y") %>%
  arrange(desc(date))


brief_entries(pd,
  what = title,
  when = date,
  with = location)

```

# Professional memberships
```{r memberships}
pm <- read_csv("data/prof_memberships.csv")

pm <- pm %>%
  # filter(., include == "Y") %>%
  arrange(desc(start)) %>% 
  mutate(start=as.Date(start, format = "%d/%m/%Y"))
         # end = as.character(end))



brief_entries(pm,
  what = group,
  when = as.character(
      glue("{month(start, label = TRUE, abbr = TRUE)} {year(start)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'Present')}")))

```


<!-- # Referees -->

<!-- ```{r refs} -->
<!-- refs<- read_csv("data/refs.csv") -->
<!-- refs <- refs %>% -->
<!--   filter(., include == "Y") %>% -->
<!--   arrange(desc(year))## condition comes from csv. change manually to include/exclude referees -->

<!-- detailed_entries(refs, -->
<!--   what = name, -->
<!--   when = role, -->
<!--   with = where, -->
<!--   where = contact) -->

<!-- ``` -->
