---
name: Dr. Micheline Campbell
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons), PhD
position: Research Associate, UNSW Sydney
address: Sydney, Australia
phone: +61 411 282 657
email: michelineleecampbell@gmail.com
# website: michelinecampbell.netlify.app
github: MichelineCampbell
twitter: michcampbell
# headcolor: 990000
headcolor: 125656
# headcolor: 000000
# date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::moderncv:
    theme: classic
    keep_tex: true
  # vitae::awesomecv:
    # latexengine: pdflatex

    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(readr)
library(tidyverse)
library(glue)
library(lubridate)
```

# Professional Summary

I have a PhD in speleothem palaeo-climatology and am currently employed as a research associate at the University of New South Wales, contributing to the Australian Research Council Discovery Project "Reconstructing Australia’s fire history from cave stalagmites". I have strong data and field science skills and have developed a research skillset applicable to a broad range of topics within the environmental sciences. My PhD research focused on stalagmite-based climate proxy records and associated karst geomorphology and groundwater hydrology, and since then I have worked in the surface hydrology and palaeoclimate-water security nexus. I am hoping to continue my career in physical geography by securing a position where I can apply skills I have developed in a meaningful way and contribute to the development of the next generation of geographers.

# Education
```{r edu1, include = FALSE}

edu.raw <- read_csv("data/education.csv")

edu.raw <- edu.raw %>%
  mutate(start_date=as.Date(start_date, format = "%d/%m/%Y")) %>%
  mutate(end_date=as.Date(end_date, format = "%d/%m/%Y")) %>%
  arrange(desc(end_date))


edu1 <- which(is.na(edu.raw$thesis))
edu2 <- edu.raw[-edu1,]

edu3 <- edu2 %>%
  mutate(pi = dplyr::if_else(!is.na(pi), glue("Supervisors: {pi}"), "Supervisor: NA"),
         thesis = dplyr::if_else(!is.na(thesis), glue(" \\textbf{Thesis: [thesis]}", .open = "[", .close = "]"),glue(NA))) %>%
  gather(thesis, pi, key = "whytype", value = "why") %>%
    arrange(desc(end_date))
edu3["why"]

edu4 <- edu.raw[edu1,]
```

```{r edu2}

detailed_entries(edu3,
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} -
           {if_else(!is.na(end_date),
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = paste(department, university, sep = ", "),
                 why = why,
                 .protect = FALSE)
detailed_entries(edu4,
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} -
           {if_else(!is.na(end_date),
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 .protect = FALSE)
```

# Experience

## Research

```{r experience}
job.titles <- read_csv("data/experience.csv")
job.descriptions <- read_csv("data/jobdesc.csv")

job.titles <- job.titles %>%
  mutate(begin=as.Date(begin, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))


job.titles %>%
  # Only 5 most recent jobs
  arrange(desc(begin)) %>%
  filter(row_number() <= 5) %>%
  # Join job descriptions
  left_join(job.descriptions) %>%
  # Arrange by descending begin date
  arrange(desc(begin)) %>%
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = glue("{dept}, {where}"),
    where = glue("{city}, {state}, {country}"),
    why = accomplishments)


```

## Teaching
```{r teaching}
fund <- read_csv("data/teaching.csv")

detailed_entries(fund,
                 when = years,
                 what = paste(role, course, sep = ": "),
                 where = location,
                 with = paste(department, university, sep = ", "),
                 .protect = FALSE) %>%
  arrange(desc(when))
```
Teaching contributions include the delivery and creation of content for undergraduate and masters level units, both in the classroom/laboratory and in the field. Catchment and River Processes, which I taught into since its inception at UWA, consistently achieved high student ratings, including in 2018 when it received a score of 3.7/4. This placed it in the 70^th^ percentile of UWA courses.

\newpage
# Funding and Scholarships
```{r funding}
fund <- read_csv("data/funding.csv")

detailed_entries(fund,
                 when = years,
                 what = paste(funder, grant),
                 why = amount,
                 .protect = FALSE) %>%
  arrange(desc(when))

```

# Publications
## Published
```{r publications}
# add in review
bibliography_entries("data/my_pubs.bib") %>%
 dplyr::arrange(desc(issued)) # bib from 'my_pubs' folder in Mendeley
```

<!-- \newpage -->
<!-- ## In Review -->
<!-- ```{r inreview} -->
<!-- # add in review -->
<!-- bibliography_entries("data/pubs_in_review.bib")# %>% -->
<!--   # dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley -->
<!-- ``` -->

<!-- ## In Preparation -->
<!-- ```{r inprep} -->
<!-- # add in review -->
<!-- bibliography_entries("data/pubs_in_prep.bib")# %>% -->
<!--   # dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley -->
<!-- ``` -->

<!-- \newpage -->
# Conference Presentations (presenting only)
```{r presentations, include =FALSE}
presentations.raw <- read_csv("data/presentations.csv")
presentations <-
  presentations.raw %>%
  mutate(when=as.Date(when, format = "%d/%m/%Y")) %>%
  arrange(desc(when))

```

## Talks
```{r talks}
presentations %>%
  filter(tag %in% c("talk")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)

```

<!-- \newpage -->

## Posters
```{r posters}
presentations %>%
  filter(tag %in% c("poster")) %>%
  arrange(desc(when)) %>%
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)
```

<!-- \newpage -->
<!-- # Skills -->

<!-- ## Statistical -->

<!-- ```{r softsskills} -->
<!-- skills.titles <- read.csv("data/skills.csv") -->
<!-- skills.descriptions <- read.csv("data/skillsdesc.csv") -->

<!-- skills.titles %>% -->
<!--   dplyr::filter(., include == "Y") %>% -->
<!--   dplyr::filter(tag %in% c("stats1")) %>% -->
<!--   # Join job descriptions -->
<!--   left_join(skills.descriptions) %>% -->
<!--   # Format as detailed entries -->
<!--   detailed_entries( -->
<!--     what = skill, -->
<!--     why = extra) -->

<!-- ``` -->

<!-- ```{r methodskills} -->
<!-- skills.titles <- read_csv("data/skills.csv") -->
<!-- skills.descriptions <- read_csv("data/skillsdesc.csv") -->

<!-- skills.titles %>% -->
<!--   filter(., include == "Y") %>% -->
<!--   filter(tag %in% c("stats2")) %>% -->
<!--   # Join job descriptions -->
<!--   left_join(skills.descriptions) %>% -->
<!--   # Format as detailed entries -->
<!--   detailed_entries( -->
<!--     what = skill, -->
<!--     why = extra) -->

<!-- ``` -->

<!-- ## Field -->
<!-- ```{r fieldskills} -->
<!-- skills.titles <- read_csv("data/skills.csv") -->
<!-- skills.descriptions <- read_csv("data/skillsdesc.csv") -->

<!-- skills.titles %>% -->
<!--   filter(., include == "Y") %>% -->
<!--   filter(tag %in% c("field")) %>% -->
<!--   # Join job descriptions -->
<!--   left_join(skills.descriptions) %>% -->
<!--   # Format as detailed entries -->
<!--   detailed_entries( -->
<!--     what = skill, -->
<!--     why = extra) -->

<!-- ``` -->

<!-- <!-- \newpage --> 
<!-- ## Other -->
<!-- ```{r otherkills} -->
<!-- skills.titles <- read_csv("data/skills.csv") -->
<!-- skills.descriptions <- read_csv("data/skillsdesc.csv") -->

<!-- skills.titles %>% -->
<!--   filter(., include == "Y") %>% -->
<!--   filter(tag %in% c("other")) %>% -->
<!--   # Join job descriptions -->
<!--   left_join(skills.descriptions) %>% -->
<!--   # Format as detailed entries -->
<!--   detailed_entries( -->
<!--     what = skill, -->
<!--     why = extra) -->

<!-- ``` -->

# Service 

```{r servics} 
service.titles <- read_csv("data/service.csv")
service.descriptions <- read_csv("data/servicedesc.csv")

service.titles <- service.titles %>%
  mutate(start = as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end = as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end)) 



service.descriptions <- service.descriptions %>%
  mutate(start=as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))

service.titles %>%
  arrange(desc(start)) %>%
  # Join job descriptions
  left_join(service.descriptions) %>%
  # Arrange by descending begin date
  arrange(desc(start)) %>%
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(start, label = TRUE, abbr = TRUE)} {year(start)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'Present')}")),
    
    
    
    # when = as.character(
#       glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} -
#            {if_else(!is.na(end),
#            paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    why = accomplishment)


```

# Completed Peer Reviews

```{r reviews}
revs <- read_csv("data/reviews.csv")

revs <- revs %>%
  filter(., include == "Y") %>%
  arrange(desc(year)) 
         # end = as.character(end))



brief_entries(revs,
  what = group,
  when = year)

```


# Professional Development
```{r pd}
pd <- read_csv("data/pd.csv")

pd <- pd %>%
  filter(., include == "Y") %>%
  arrange(desc(date))


brief_entries(pd,
  what = title,
  when = date,
  with = location)

```

# Professional Memberships
```{r memberships}
pm <- read_csv("data/prof_memberships.csv")

pm <- pm %>%
  # filter(., include == "Y") %>%
  arrange(desc(start)) %>% 
  mutate(start=as.Date(start, format = "%d/%m/%Y"))
         # end = as.character(end))



brief_entries(pm,
  what = group,
  when = as.character(
      glue("{month(start, label = TRUE, abbr = TRUE)} {year(start)} -
           {if_else(!is.na(end),
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'Present')}")))

```


# Referees

```{r refs}
refs<- read_csv("data/refs.csv")
refs <- refs %>%
  filter(., include == "Y") %>%
  arrange(desc(year))## condition comes from csv. change manually to include/exclude referees

detailed_entries(refs,
  what = name,
  when = role,
  with = where,
  where = contact)

```
