---
name: Dr. Micheline Campbell
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons), PhD
position: Scientist, QLD Dept. of Natural Resources, Mines, and Energy
address: Rockhampton, Australia
phone: +61 411 282 657
# www: mariecurie.com
email: michelineleecampbell@gmail.com
# website: mitchelloharawild.com
github: MichelineCampbell
twitter: michcampbell_
headcolor: 414141
# date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
  # vitae::awesomecv:
    theme: classic
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(readr)
library(tidyverse)
library(glue)
```

# Professional Summary 

I am a former climatologist, currently working in hydrological sediment and nutrient transport. I have strong data science skills and have developed research skills applicable to a broad range of topics within the environmental sciences. My PhD research focused on stalagmite-based climate proxy records and associated karst geomorphology and groundwater hydrology, while my current position with the Queensland Department of Natural Resources, Mining, and Energy has a strong focus on field experiments and hypothesis testing of reducing nutrient and sediment runoff to Great Barrier Reef catchments. I am hoping to further my scientific career by securing a position where I can continue to use the skills I have developed, broaden my skillset, and continue teaching and engaging with undergraduate and postgraduate students. 

# Experience

## Research

## Teaching

# Education
```{r edu1, include = FALSE}
edu.raw <- read_csv("data/education.csv")
edu1 <- which(is.na(edu.raw$thesis))
edu2 <- edu.raw[-edu1,]

edu3 <- edu2 %>% 
  mutate(pi = dplyr::if_else(!is.na(pi), glue("Supervisors: {pi}"), "Supervisor: NA"),
         thesis = dplyr::if_else(!is.na(thesis), glue(" \\textbf{Thesis: [thesis]}", .open = "[", .close = "]"),glue(NA))) %>% 
  gather(thesis, pi, key = "whytype", value = "why")
edu3["why"] 

edu4 <- edu.raw[edu1,] 
```

```{r edu2}
detailed_entries(edu3, 
                 when = glue("{start_date}--{end_date}"),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 why = why,
                 .protect = FALSE) %>% 
  arrange(desc(when))
detailed_entries(edu4, 
                 when = glue("{start_date}--{end_date}"),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 .protect = FALSE)
```

# Publications
```{r publications}
# add in review
bibliography_entries("data/my_pubs.bib") %>% 
  dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley
```

# Funding and Scholarships

# Conference Presentations

# Skills

# Service
## Volunteer Positions

## Presented Workshops

# Professional Development

# References
```{r refs}
refs<- read_csv("data/refs.csv")
refs <- refs %>% 
  filter(., include == "Y") ## condition comes from csv. change manually to include/exclude referees

detailed_entries(refs,
  what = name,  
  when = role,
  with = where,
  where = contact)

```


<!-- # ```{r refs} -->
<!-- # tribble( -->
<!-- #   ~Name, ~Title, ~Contact, -->
<!-- #   'Dr. Nik Callow',  "Senior Lecturer, School of Agriculture and Environment, The University of Western Australia", "nik.callow@uwa.edu.au; +61 8 6488 1924", -->
<!-- #   'Professor Hamish McGowan',  "School of Earth and Environmental Sciences, The University of Queensland", "h.mcgowan@uq.edu.au", -->
<!-- #   'Dr. Gavan McGrath',"Research Hydrologist, WA Dept. of Biodiversity Conservations and Attractions", "gavan.mcgrath@dbca.wa.gov.au", -->
<!-- #   'Bronwyn Bosomworth',  "A/Senior Scientist Land and Water Science, QLD Dept. of Natural Resources, Mining, and Energy", "bronwyn.bosomworth@dnrme.qld.gov.au" -->
<!-- # ) %>%  -->
<!-- #   detailed_entries( -->
<!-- #     what = Name,  -->
<!-- #     with = Title, -->
<!-- #     where = Contact -->
<!-- #   ) -->
<!-- # ``` -->

