---
name: Dr. Micheline Campbell
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons), PhD
position: Scientist, QLD Dept. of Natural Resources, Mines, and Energy
address: Rockhampton, Australia
phone: +61 411 282 657
# www: mariecurie.com
email: michelineleecampbell@gmail.com
# website: mitchelloharawild.com
github: MichelineCampbell
twitter: michcampbell_
headcolor: 414141
# date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
  # vitae::awesomecv:
    theme: classic
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(readr)
library(tidyverse)
library(glue)
library(lubridate)
```

# Professional Summary 

I have a PhD in palaeo-climatology and am currently working in hydrological sediment and nutrient transport. I have strong data science skills and have developed research skills applicable to a broad range of topics within the environmental sciences. My PhD research focused on stalagmite-based climate proxy records and associated karst geomorphology and groundwater hydrology, while my current position with the Queensland Department of Natural Resources, Mining, and Energy has a strong focus on field experiments and hypothesis testing of reducing nutrient and sediment runoff to Great Barrier Reef catchments. I am hoping to further my scientific career by securing a position where I can continue to use the skills I have developed, broaden my skillset, and continue teaching and engaging with undergraduate and postgraduate students. 

# Experience

<!-- ## Research  -->
<!-- ```{r experience} -->
<!-- experience <- read_csv("data/experience.csv") -->

<!-- experience <- experience %>%  -->
<!--   mutate(begin=as.Date(begin, format = "%d/%m/%Y")) %>%  -->
<!--   mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%  -->
<!--   arrange(desc(end)) -->

<!-- detailed_entries(experience, -->
<!--     what = glue("{role}, {where}"), -->
<!--     when = as.character( -->
<!--       glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} -  -->
<!--            {if_else(!is.na(end),  -->
<!--            paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")), -->
<!--     # with = employer, -->
<!--     where = glue("{city}, {state}, {country}"))#, -->
<!--     # why = accomplishments)               -->


<!-- ``` -->

```{r experience 2}
job.titles <- read_csv("data/experience.csv")
job.descriptions <- read_csv("data/jobdesc.csv")

job.titles <- job.titles %>% 
  mutate(begin=as.Date(begin, format = "%d/%m/%Y")) %>% 
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>% 
  arrange(desc(end))


job.titles %>% 
  # Only 5 most recent jobs
  arrange(desc(begin)) %>% 
  filter(row_number() <= 5) %>% 
  # Join job descriptions
  left_join(job.descriptions) %>% 
  # Arrange by descending begin date
  arrange(desc(begin)) %>% 
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - 
           {if_else(!is.na(end), 
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = dept,
    where = glue("{city}, {state}, {country}"),
    why = accomplishments)


```








## Teaching 
```{r teaching}
fund <- read_csv("data/teaching.csv")

detailed_entries(fund, 
                 when = years,
                 what = paste(role, course),
                 where = university,
                 .protect = FALSE) %>% 
  arrange(desc(when))
```


# Education
```{r edu1, include = FALSE}
edu.raw <- read_csv("data/education.csv")
edu1 <- which(is.na(edu.raw$thesis))
edu2 <- edu.raw[-edu1,]

edu3 <- edu2 %>% 
  mutate(pi = dplyr::if_else(!is.na(pi), glue("Supervisors: {pi}"), "Supervisor: NA"),
         thesis = dplyr::if_else(!is.na(thesis), glue(" \\textbf{Thesis: [thesis]}", .open = "[", .close = "]"),glue(NA))) %>% 
  gather(thesis, pi, key = "whytype", value = "why")
edu3["why"] 

edu4 <- edu.raw[edu1,] 
```

```{r edu2}
detailed_entries(edu3, 
                 when = glue("{start_date}--{end_date}"),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 why = why,
                 .protect = FALSE) %>% 
  arrange(desc(when))
detailed_entries(edu4, 
                 when = glue("{start_date}--{end_date}"),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 .protect = FALSE)
```

# Publications
```{r publications}
# add in review
bibliography_entries("data/my_pubs.bib") %>% 
  dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley
```

# Funding and Scholarships
```{r funding}
fund <- read_csv("data/funding.csv")

detailed_entries(fund, 
                 when = years,
                 what = paste(funder, grant),
                 where = amount,
                 .protect = FALSE) %>% 
  arrange(desc(when))

```


# Conference Presentations

# Skills

# Service
## Volunteer Positions

## Presented Workshops

# Professional Development
```{r pd}
pd <- read_csv("data/pd.csv")

pd <- pd %>%
  filter(., include == "Y") %>% 
  arrange(desc(date))


detailed_entries(pd,
  what = title,
  when = date,
  with = location) 

```

# References
```{r refs}
refs<- read_csv("data/refs.csv")
refs <- refs %>% 
  filter(., include == "Y") ## condition comes from csv. change manually to include/exclude referees

detailed_entries(refs,
  what = name,  
  when = role,
  with = where,
  where = contact)

```


<!-- # ```{r refs} -->
<!-- # tribble( -->
<!-- #   ~Name, ~Title, ~Contact, -->
<!-- #   'Dr. Nik Callow',  "Senior Lecturer, School of Agriculture and Environment, The University of Western Australia", "nik.callow@uwa.edu.au; +61 8 6488 1924", -->
<!-- #   'Professor Hamish McGowan',  "School of Earth and Environmental Sciences, The University of Queensland", "h.mcgowan@uq.edu.au", -->
<!-- #   'Dr. Gavan McGrath',"Research Hydrologist, WA Dept. of Biodiversity Conservations and Attractions", "gavan.mcgrath@dbca.wa.gov.au", -->
<!-- #   'Bronwyn Bosomworth',  "A/Senior Scientist Land and Water Science, QLD Dept. of Natural Resources, Mining, and Energy", "bronwyn.bosomworth@dnrme.qld.gov.au" -->
<!-- # ) %>%  -->
<!-- #   detailed_entries( -->
<!-- #     what = Name,  -->
<!-- #     with = Title, -->
<!-- #     where = Contact -->
<!-- #   ) -->
<!-- # ``` -->

