---
name: Dr. Micheline Campbell
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: BA(Hons), PhD
position: Postdoctoral Researcher, University College Dublin
address: Brisbane, Australia (due to covid-19)
phone: +61 411 282 657
# www: mariecurie.com
email: michelineleecampbell@gmail.com
# website: mitchelloharawild.com
github: MichelineCampbell
twitter: michcampbell
headcolor: 414141
# date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
  # vitae::awesomecv:
    theme: classic
    keep_tex: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(scholar)
library(readr)
library(tidyverse)
library(glue)
library(lubridate)
```

# Professional Summary 

I have a PhD in palaeo-climatology and am currently employed as a postdoctoral researcher at University College Dublin, researching the palaeoclimate of eastern Australia, with a focus on water security. I have strong data science skills and have developed research skills applicable to a broad range of topics within the environmental sciences. My PhD research focused on stalagmite-based climate proxy records and associated karst geomorphology and groundwater hydrology, while my current position is focused on exploring future water security by expanding our knowledge of the palaeo-environment of eastern Australia. I am hoping to continue my career in climate and hydrology area by securing a position where I can apply skills I have developed, develop new skills, and continue to engage with students and industry partners.  

# Education
```{r edu1, include = FALSE}

edu.raw <- read_csv("data/education.csv")

edu.raw <- edu.raw %>% 
  mutate(start_date=as.Date(start_date, format = "%d/%m/%Y")) %>% 
  mutate(end_date=as.Date(end_date, format = "%d/%m/%Y")) %>% 
  arrange(desc(end_date))


edu1 <- which(is.na(edu.raw$thesis))
edu2 <- edu.raw[-edu1,]

edu3 <- edu2 %>% 
  mutate(pi = dplyr::if_else(!is.na(pi), glue("Supervisors: {pi}"), "Supervisor: NA"),
         thesis = dplyr::if_else(!is.na(thesis), glue(" \\textbf{Thesis: [thesis]}", .open = "[", .close = "]"),glue(NA))) %>% 
  gather(thesis, pi, key = "whytype", value = "why") %>% 
    arrange(desc(end_date))
edu3["why"] 

edu4 <- edu.raw[edu1,] 
```

```{r edu2}

detailed_entries(edu3, 
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} - 
           {if_else(!is.na(end_date), 
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = paste(department, university, sep = ", "),
                 why = why,
                 .protect = FALSE) 
detailed_entries(edu4, 
                 when = as.character(glue("{month(start_date, label = TRUE, abbr = TRUE)} {year(start_date)} - 
           {if_else(!is.na(end_date), 
           paste(month(end_date, label = TRUE, abbr = TRUE), year(end_date)), 'present')}")),
                 what = paste0(degree," (", major, ")"),
                 # what2 = major,
                 where = location,
                 with = university,
                 .protect = FALSE)
```

# Experience

## Research

```{r experience}
job.titles <- read_csv("data/experience.csv")
job.descriptions <- read_csv("data/jobdesc.csv")

job.titles <- job.titles %>% 
  mutate(begin=as.Date(begin, format = "%d/%m/%Y")) %>% 
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>% 
  arrange(desc(end))


job.titles %>% 
  # Only 5 most recent jobs
  arrange(desc(begin)) %>% 
  filter(row_number() <= 5) %>% 
  # Join job descriptions
  left_join(job.descriptions) %>% 
  # Arrange by descending begin date
  arrange(desc(begin)) %>% 
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - 
           {if_else(!is.na(end), 
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = glue("{dept}, {where}"),
    where = glue("{city}, {state}, {country}"),
    why = accomplishments)


```

## Teaching 
```{r teaching}
fund <- read_csv("data/teaching.csv")

detailed_entries(fund, 
                 when = years,
                 what = paste(role, course, sep = ": "),
                 where = location,
                 with = paste(department, university, sep = ", "),
                 .protect = FALSE) %>% 
  arrange(desc(when))
```
Teaching contributions include the delivery and creation of content for undergraduate and masters level units, both in the classroom/laboratory and in the field. Catchment and River Processes, which I taught into since its inception at UWA, consistently achieved high student ratings, including in 2018 when it received a score of 3.7/4. This placed it in the 70^th^ percentile of UWA courses.

# Funding and Scholarships
```{r funding}
fund <- read_csv("data/funding.csv")

x<- detailed_entries(fund,
                 when = years,
                 what = paste(funder, grant),
                 why = amount,
                 .protect = FALSE) %>%
  arrange(desc(when))
x
```

# Publications
## Published
```{r publications}
# add in review
bibliography_entries("data/my_pubs.bib") %>% 
 dplyr::arrange(desc(issued)) # bib from 'my_pubs' folder in Mendeley
```

<!-- ## In Review -->
<!-- ```{r inreview} -->
<!-- # add in review -->
<!-- bibliography_entries("data/pubs_in_review.bib")# %>%  -->
<!--   # dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley -->
<!-- ``` -->

## In Preparation
```{r inprep}
# add in review
bibliography_entries("data/pubs_in_prep.bib")# %>%
  # dplyr::arrange(desc(year)) # bib from 'my_pubs' folder in Mendeley
```

# Conference Presentations
```{r presentations, include =FALSE}
presentations.raw <- read_csv("data/presentations.csv")
presentations <- 
  presentations.raw %>% 
  mutate(when=as.Date(when, format = "%d/%m/%Y")) %>% 
  arrange(desc(when))

```

## Talks
```{r talks}
presentations %>%  
  filter(tag %in% c("talk")) %>% 
  arrange(desc(when)) %>% 
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)

```

\newpage

## Posters
```{r posters}
presentations %>%  
  filter(tag %in% c("poster")) %>% 
  arrange(desc(when)) %>% 
  detailed_entries(what = title,
                   when = glue("{month(when, label = TRUE)} {year(when)}"),
                   with = paste(conference,location, sep = ", "),
                   where = authors,
                   .protect = FALSE)
```

# Skills

## Statistical

```{r softsskills}
skills.titles <- read.csv("data/skills.csv")
skills.descriptions <- read.csv("data/skillsdesc.csv")

skills.titles %>%
  dplyr::filter(., include == "Y") %>%
  dplyr::filter(tag %in% c("stats1")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

```{r methodskills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("stats2")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

## Field
```{r fieldskills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("field")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

\newpage
## Other
```{r otherkills}
skills.titles <- read_csv("data/skills.csv")
skills.descriptions <- read_csv("data/skillsdesc.csv")

skills.titles %>%
  filter(., include == "Y") %>%
  filter(tag %in% c("other")) %>%
  # Join job descriptions
  left_join(skills.descriptions) %>%
  # Format as detailed entries
  detailed_entries(
    what = skill,
    why = extra)

```

# Service

```{r servics}
service.titles <- read_csv("data/service.csv")
service.descriptions <- read_csv("data/servicedesc.csv")

service.titles <- service.titles %>%
  mutate(start=as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))

service.descriptions <- service.descriptions %>%
  mutate(start=as.Date(start, format = "%d/%m/%Y")) %>%
  mutate(end=as.Date(end, format = "%d/%m/%Y")) %>%
  arrange(desc(end))

service.titles %>%
  arrange(desc(start)) %>%
  # Join job descriptions
  left_join(service.descriptions) %>%
  # Arrange by descending begin date
  arrange(desc(end)) %>%
  # Format as detailed entries
  detailed_entries(
    what = role,
    when = as.character(
      glue("{month(start, label = TRUE, abbr = TRUE)} {year(start)} -
           {month(end, label = TRUE, abbr = TRUE)} {year(end)}")),
    why = accomplishment)


```

# Professional Development
```{r pd}
pd <- read_csv("data/pd.csv")

pd <- pd %>%
  filter(., include == "Y") %>% 
  arrange(desc(date))


brief_entries(pd,
  what = title,
  when = date,
  with = location) 

```

# Referees

```{r refs}
refs<- read_csv("data/refs.csv")
refs <- refs %>%
  filter(., include == "Y") ## condition comes from csv. change manually to include/exclude referees

detailed_entries(refs,
  what = name,
  when = role,
  with = where,
  where = contact)

```
